[Re] Predicting metabolic biomarkers of human inborn errors of metabolism

### 2018-02-15 article/Mondeel_Ogundipe_Westerhoff-2017.tex
RE: federico
Inclusion of figure 3

@@

The results summarized in Figures 1 and 2 of \autocite{Shlomi2009} have
been successfully replicated with the software tools provided here.
Overall, the reproduction process went smoothly, since the method was
applied to both an illustrative example and to the human metabolic
reconstruction, resulting in a multitude of test cases for the
implementation.

>>>>

\subsection{\texorpdfstring{Reproduction of Figure 3
\autocite{Shlomi2009}}{Reproduction of Figure 3 {[}@Shlomi2009{]}}}\label{reproduction-of-figure-3-shlomi2009}

\begin{figure}
\centering
\includegraphics{Figures/Reproduction_Shlomi_fig_3}
\caption{Reproduction of Figure 3 in \autocite{Shlomi2009}. (A)
Illustration of the subnetwork of Recon 1 relevant to the effect of
homocystinuria on the metabolism and transport of methionine. Nodes
represent metabolites and edges represent reactions. For simplicity,
only abbreviations of metabolite names are given in the Figure. The full
names are: L-Methionine (met), S-Adenosyl-L-methionine (amet),
S-Adenosyl-L-homocysteine (ahcys), L-Homocysteine (hcys), L-Serine
(ser), L-Cystathionine (cyst), L-Cysteine (cys),
S-Adenosylmethioninamine (ametam), 5-Methylthioadenosine (5mta),
5-Methylthio-5-deoxy-D-ribose 1-phosphate (5mdr1p),
5-Methylthio-5-deoxy-D-ribulose 1-phosphate (dmdru1p),
2,3-diketo-5-methylthio-1-phosphopentane (dkmpp),
2-keto-4-methylthiobutyrate (2kmb). Metabolites with a green background
color participate in additional reactions not shown here. Reactions are
indicated by their identifiers in Recon 1 and with a corresponding
enzyme commision number if available. We highlighted the mutations for
Homocystinuria (dysfunctional CBS) and hypermethioninemia (dysfunctional
AHCY). (B) Prediction of concentration changes of methionine in
homocystinuria and S-adenosylhomocysteine hydrolase deficiency based on
the biomarker prediction algorithm.}\label{fig:Shlomi2009_figure_3}
\end{figure}

Figure 3 in the original publication entailed an in-depth look at the
results highlighted in Figure 2 for methionine metabolism. We reproduced
this Figure as Figure ~\ref{fig:Shlomi2009_figure_3}. The numerical
results illustrated in ~\ref{fig:Shlomi2009_figure_3}B may be reproduced
using the notebook `Reproduce\_figure2\_Shlomi2009', the detailed
results may be inspected using the last cell of that notebook. We note
that in the original publication the WT interval for the CBS IEM was
drawn as an interval whereas our results indicate an interval of
\([-1,-1]\).

@@

The results summarized in Figures 1 (panel A and B), 2 and 3 of
\autocite{Shlomi2009} have been successfully replicated with the
software tools provided here. Overall, the reproduction process went
smoothly, since the method was applied to both an illustrative example
and to the human metabolic reconstruction, resulting in a multitude of
test cases for the implementation.
